The Promise that R makes

### 2019-03-07 report/report.Rmd
Add summarization, visualization and reporting for escaped argument

>>>>

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_function_call_count_by_return_value_type")
```

```{r echo = FALSE}
show_table("escaped_argument_function_call_count_by_return_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_function_count_by_return_value_type")
```

```{r echo = FALSE}
show_table("escaped_argument_function_count_by_return_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_function_count_by_category")
```

```{r echo = FALSE}
show_table("escaped_argument_function_count_by_category")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_nature")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_nature")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_dispatch_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_dispatch_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_expression_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_expression_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_value_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_value_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_force_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_force_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_metaprogram_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_metaprogram_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_lookup_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_lookup_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_direct_self_scope_mutation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_direct_self_scope_mutation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_indirect_self_scope_mutation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_indirect_self_scope_mutation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_direct_lexical_scope_mutation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_direct_lexical_scope_mutation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_indirect_lexical_scope_mutation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_direct_non_lexical_scope_mutation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_indirect_non_lexical_scope_mutation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_direct_self_scope_observation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_direct_self_scope_observation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_indirect_self_scope_observation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_indirect_self_scope_observation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_direct_lexical_scope_observation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_direct_lexical_scope_observation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_indirect_lexical_scope_observation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_indirect_lexical_scope_observation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_direct_non_lexical_scope_observation_type")
```

```{r echo = FALSE, out.width="1000px"}
show_graph("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
```

```{r echo = FALSE}
show_table("escaped_argument_count_by_indirect_non_lexical_scope_observation_type")
```
